Generalizations of Quotient Inductive-Inductive Types\thanks{This work was supported by EFOP-3.6.3-VEKOP-16-2017-00002 grant and COST Action EUTypes CA15123.}

### 2019-10-17 draft/paper.tex
progress

In the following sections, we will consider QIIT algebras at arbitrary finite
levels, along with large eliminations, where the initial algebra can be at a
different level than the target algebra. For a simple example, consider natural
number algebras at a given level $i$, given as the $\Sigma$-type $NatAlg_i :\equiv(Nat :
\Set_i)\times Nat\times(Nat \ra Nat)$. The initial such algebra is the set of
natural numbers, which is at level $0$, but in type theory we often want to
eliminate into larger $\Set_i$, for example when computing a $Nat$-indexed family
of types.

Universe levels are usually viewed as a bureaucratic and tedious part of type
theory, and are often omitted or mentioned only in passing. Here we intend to
model universe levels in a precise way, because large eliminations are an
essential part of the practical usage of inductive types. Hence, we need a way
to conveniently reason about levels without too much administrative
burden. Unfortunately, simple universe setups are insufficient for this
purpose. We need two features: cumulativity and a way to quantify over finite
levels.

@@

Cumulativity makes handling of algebras and constructions at different levels
much easier. For example, given an algebra $\gamma : NatAlg_i$, cumulativity
allows us to also have $\gamma : NatAlg_{i+j}$. In a non-cumulative setting such
as Agda, we may only have for each type $A : \Set_i$ a type $\mathsf{Lift}_{i\,j}\,A :
\Set_{i+j}$ which is isomorphic to $A$ up to definitional equality.

In the most basic form, cumulativity requires that whenever $A : \Set_i$, then
also $A : \Set_{i+j+1}$. However, the $NatAlg$ example above also required a
form of cumulativity for $\Sigma$ and $\Pi$ types, which we also need in general
for QIIT algebras.

@@

We extend the base theory with an extensional identity type, $\Sigma$-types and
the unity type. In \cite{TODO} a proof of canonicity is provided for the base
theory, which also includes a standard set-theoretic model. It is
straightforward to extend the canonicity proof to cover our additional type
formers.

@@

We also have a lifting operation on types, which introduces cumulativity.

\begin{figure}
\begin{mathpar}
  \inferrule*[lab=universe formation]
             {\\}
             {\Gamma \vdash \Set_i : \Set_{i+j+1}}

  \inferrule*[lab=type lifting]
             {\Gamma \vdash A : \Set_i}
             {\Gamma \vdash\,\Lift_j A : \Set_{i+j+1}}

  \inferrule*[lab=universe lifting]{}{\Lift_j \Set_i = \Set_{i+j}}

  \inferrule*[lab=term lifting]
             {}
             {\{t\,|\,\Gamma \vdash t : A\} = \{t\,|\,\Gamma \vdash t :\,\,\Lift_j A\}}

  \inferrule*[lab=context lifting]
             {}
             {(\Gamma,\,x : A) = (\Gamma,\,x :\,\,\Lift_j A)}

  \inferrule*[lab=function lifting]
             {}
             {\Lift_j((x : A)\ra B) = (x :\,\Lift_j A)\ra\,\Lift_j B}

  \inferrule*[lab=pair lifting]
             {}
             {\Lift_j((x : A)\times B) = (x :\,\Lift_j A)\,\times\Lift_j B}
\end{mathpar}

@@

In Figure \ref{lifting}, we include an excerpt of Sterling's rules, with a
slight change of presentation. We lift from $i$ to $i+j+1$ levels instead of
assuming $i < j$ and lifting to $j$. We also omit rules for naturality and
substitution of lifting. In general, we can expect that lifting never impedes
constructions, because it appropriately computes out of the way.

@@

We also need to quantify over universe levels. cETT does not support this, and
we leave it like that. Instead, for the sake of simplicity, we quantify over
levels in an unspecified metatheory \emph{outside} cETT. Hence, a universe
polymorphic cETT term is understood as a $\mathbb{N}$-indexed family of
terms. We use the $\forall$ symbol for this, e.g.\ as $\forall\,i.\,\Set_i \ra
\Set_i$. This is sufficient in this paper, because we do not need to internalize
level-polymorphic constructions in cETT.

@@

\begin{nidefinition}{Notion of model for ToS.}\label{def:tos}
For levels $i$ and $j$, there is a cETT type $\ToS_{i,j} : \Set_{\max(i,\,j)+1}$, whose elements are
ToS models (or ToS-algebras). $\ToS_{i,j}$ is an iterated $\Sigma$-type, containing
all of the following components.
\begin{enumerate}
\item
  A category with families (CwF), where all four underlying sets (of
  objects, morphisms, types and terms) are in $\Set_i$. Following notation in
  \cite{TODO}, we denote these respectively as $\Con : \Set_i$, $\Sub : \Con \ra
  \Con \ra \Set_i$, $\Ty : \Con \ra \Set_i$ and $\Tm : (\Gamma : \Con) \ra
  \Ty\,\Gamma \ra \Set_i$. We denote the empty context as $\emptycon : \Con$,
  context extension as $\blank\ext\blank : (\Gamma : \Con)\ra \Ty\,\Gamma \ra \Con$.
  Substitution on types and terms is written as $\blank[\blank]$.
\item
  A universe $\U : \Ty\,\Gamma$ with decoding $\El : (a : \Tm\,\Gamma\,\U) \ra
  \Ty\,\Gamma$.
\item
  Inductive function space, with $\Pii : (a : \Tm\,\Gamma\,\U) \ra
  \Ty\,(\Gamma\,\ext\,\El\,a) \ra \Ty\,\Gamma$, application as $\appi :
  \Tm\,\Gamma\,(\Pii\,a\,B)\ra \Tm\,(\Gamma\,\ext\,\El\,a)\,B$, and its inverse
  $\lami$.
\item
  External function space with $\Set_j$ domain: $\Pie : (A : \Set_j)\ra(A \ra
  \Ty\,\Gamma)\ra \Ty\,\Gamma$, with $\appe : \Tm\,\Gamma\,(\Pie\,A\,B)\ra(x :
  A)\ra \Tm\,\Gamma\,(B\,x)$, and likewise $\lame$ as inverse.
\item
  Infinitary function space, with $\Piinf : (A : \Set_j)\ra(A \ra
  \Tm\,\Gamma\,\U)\ra \Tm\,\Gamma\,\U$, $\appinf :
  \Tm\,\Gamma\,(\El\,(\Pie\,A\,b))\ra(x : A)\ra \Tm\,\Gamma\,(\El\,(b\,x))$, and
  $\laminf$.
\item
  An identity type $\Id : (a : \Tm\,\Gamma\,\U)\ra
  \Tm\,\Gamma\,(\El\,a)\ra\Tm\,\Gamma\,(\El\,a)\ra \Tm\,\Gamma\,\U$, with
  $\Refl : (T : \Tm\,\Gamma\,(\El\,a))\ra \Id\,a\,t\,t$, equality reflection
  and uniqueness of identity proofs.
\item
  An identity type $\IdU : \Tm\,\Gamma\,\U \ra \Tm\,\Gamma\,\U \ra \Ty\,\Gamma$, with
  evident $\ReflU$, equality reflection and uniqueness of identity proofs.
\end{enumerate}
\end{nidefinition}
In the above listing, we omit most CwF components and equations for substitution and
$\beta\eta$-conversion, but these should be understood to be also part of $\ToS_{i,j}$.

%% \paragraph{Notational conventions.}
\emph{Notational conventions.} CwF components by default support de Bruijn
indices, which are not easily readable. We use instead a nameful notation for
binders in context extension, $\Pii$ and $\lami$, e.g.\ as $(\emptycon \ext a :
U \ext t : \El\,a)$. We also define a type-theoretic version of $\appi$ for
convenience:
\begin{alignat*}{3}
  & \blank\appitt\blank && :
      \Tm\,\Gamma\,(\Pii\,a\,B)\ra
      (u : \Tm\,\Gamma\,(\El\,a)) \ra \Tm\,\Gamma\,(B[id, u])\\
  & t\appitt u && :\equiv (\appi\,t)[id, u]
\end{alignat*}

\begin{nidefinition}{Notion of signature.}
A QIIT signature at level $j$ is a context in an arbitrary $M : \ToS_{i,j}$
model. We define the type of such signatures as follows:
\[
  \Sig_j :\equiv \forall i.\,(M : \ToS_{i,j})\ra M.Con
\]

Note that $\Sig_j$ is defined as a universe-polymorphic type, so it does not
have a type internally to cETT. A concrete signature $sig$ at level $j$ has type
$\forall i.\,(M : \ToS_{i,j})\ra M.Con$, so it builds up a context from the
components of an arbitrary $\ToS$ model.

\begin{example}
The signature for natural
numbers is the following, where $\emptycon$, $\blank\ext\blank$, $\U$, $\El$ and
$\Pii$ all refer to components of the $\lambda$-bound $M$:
\begin{alignat*}{3}
  & NatSig : \Sig_0 \\
  & NatSig :\equiv \lambda (M : \ToS_{i,0}). (\emptycon\,\ext\, N : \U \,\ext\, zero : \El\,N \ext suc : \Pii\,(n : N)\,(\El\,N))
\end{alignat*}
\end{example}

The $j$ level in $\Sig_j$ specifies the level of the external types appearing in
a signatures, since the $\Pie$ and $\Piinf$ function spaces have domains in $\Set_j$.
In the case of naturals numbers, no external types appear, so the level of $NatSig$
can be chosen as $0$.

With this, we are able to specify QIITs, and we can also interpret each
signature in an arbitrary ToS model, just by applying a signature to a model.
$\Sig_j$ can be viewed as a precursor to a Church-encoding for the theory of
signatures, but we only need contexts encoded in this way, and not other ToS
components. In functional programming, this encoding is sometimes called
``finally tagless''\cite{TODO}, and it is used for defining and interpreting
embedded languages.
\end{nidefinition}

@@

\begin{example}{Infinitary constructors}. The universe $\U$ is closed under
the $\Piinf$ function type, which makes it possible to write such functions
in the domains of $\Pii$ types. This allows a signature for $W$-types, given
arbitrary $S : \Set_i$ and $P : S \ra \Set_i$ types for shapes and positions.
\[
WSig :\equiv
\emptycon \ext W : \U \ext sup : \Pie\,S\,(\lambda s.\,\Pii\,(\Piinf\,(P\,s)\,\lambda \_.\,W) \,(\El\,W))
\]
\end{example}

@@

So, why do we use flCwF instead of lex categories? After all, the former
structure has more components and has more immediate complexity than the
latter. The reason is that flCwFs allow us to define induction in strictly the
same way as one would write it down in type theory, since we have $\Ty$ and
$\Tm$ for a primitive notion of dependent objects and morphisms. In contrast,
dependent objects in lex categories is a derived notion, and the induction
principles we get are what we want only up to isomorphisms. This issue is
perhaps not very relevant to those with a purely categorical perspective, but we
are concerned with eventually implementing QIITs in proof assistants, so we
prefer if our semantics computes notions strictly.

\begin{nidefinition}{flCwF model for ToS.} For $i$ and $j$ levels, there is
an $M : \ToS_{1+\max(i+1,j),j}$ such that $M.\Con = \flCwF_{\max(i+1,j)}$.

\todo{flip level indices in ToS, maybe shorten cETT part, add more explanation
      on role of i,j in ToS(i,j)}

>>>>

In the following sections, we will consider QIIT algebras at arbitrary finite
levels, along with large eliminations, where the initial algebra can be at a
different level than the target algebra. For a simple example, consider natural
number algebras at a given level $i$, given as the $\Sigma$-type $NatAlg_i
:\equiv(Nat : \Set_i)\times Nat\times(Nat \ra Nat)$. The initial such algebra is
the set of natural numbers, which is at level $0$, but in type theory we often
want to eliminate into larger $\Set_i$, for example when computing a
$Nat$-indexed family of types. To support convenient reasoning about levels in
this paper, we need two features: cumulativity and a way to quantify over finite
levels.

%% Universe levels are usually viewed as a bureaucratic and tedious part of type
%% theory, and are often omitted or mentioned only in passing. Here we intend to
%% model universe levels in a precise way, because large eliminations are an
%% essential part of the practical usage of inductive types. Hence, we need a way
%% to conveniently reason about levels without too much administrative
%% burden. Unfortunately, simple universe setups are insufficient for this
%% purpose. We need two features: cumulativity and a way to quantify over finite
%% levels.

@@

%% Cumulativity makes handling of algebras and constructions at different levels
%% much easier. For example, given an algebra $\gamma : NatAlg_i$, cumulativity
%% allows us to also have $\gamma : NatAlg_{i+j}$. In a non-cumulative setting such
%% as Agda, we may only have for each type $A : \Set_i$ a type $\mathsf{Lift}_{i\,j}\,A :
%% \Set_{i+j}$ which is isomorphic to $A$ up to definitional equality.

We need cumulativity to reduce administrative overhead. In the most basic form,
cumulativity requires that whenever $A : \Set_i$, and $i < j$ then also $A :
\Set_j$. We also need cumulativity for $\Sigma$ and function types, in order to
have cumulativity for algebras in general. For example, we want to have $\gamma
: NatAlg_j$ whenever $\gamma : NatAlg_i$ and $i < j$.

%% However, the $NatAlg$ example above also required a form of
%% cumulativity for $\Sigma$ and $\Pi$ types, which we also need in general for
%% QIIT algebras.

@@

We extend the base theory with an extensional identity type, $\Sigma$-types and
the unit type. In \cite{TODO} a proof of canonicity is provided for the base
theory, which also includes a standard set-theoretic model. It is
straightforward to extend the canonicity proof to cover our additional type
formers.

@@

We also have a lifting operation on types, which introduces cumulativity.
\vspace{-1.5em}
\begin{figure}
\begin{mathpar}
  \inferrule*[lab=universe formation]
             {\\}
             {\Gamma \vdash \Set_i : \Set_{i+j+1}}

  \inferrule*[lab=function formation]
             {\Gamma \vdash A : \U_i \\ \Gamma,\,x : A \vdash B : \U_j}
             {\Gamma \vdash (x : A)\ra B : \U_{\max(i,j)} }

  \inferrule*[lab=$\Sigma$ formation]
             {\Gamma \vdash A : \U_i \\ \Gamma,\,x : A \vdash B : \U_j}
             {\Gamma \vdash (x : A)\times B : \U_{\max(i,j)} }

  \inferrule*[lab=unit formation]
             {\\}
             {\Gamma \vdash \top : \Set_i}

  \inferrule*[lab=type lifting]
             {\Gamma \vdash A : \Set_i \\ i < j}
             {\Gamma \vdash\,\Lift_j A : \Set_{j}}

  \inferrule*[lab=lift composition]{}{\Lift_j (\Lift_i A) =\,\,\Lift_{j} A}

  \inferrule*[lab=term lifting]
             {}
             {\{t\,|\,\Gamma \vdash t : A\} = \{t\,|\,\Gamma \vdash t :\,\,\Lift_i A\}}

  \inferrule*[lab=context lifting]
             {}
             {(\Gamma,\,x : A) = (\Gamma,\,x :\,\,\Lift_i A)}

  \inferrule*[lab=universe lifting]{}{\Lift_j \Set_i = \Set_i}

  \inferrule*[lab=function lifting]
             {}
             {\Lift_i((x : A)\ra B) = (x :\,\Lift_i A)\ra\,\Lift_i B}

  \inferrule*[lab=pair lifting]
             {}
             {\Lift_i((x : A)\times B) = (x :\,\Lift_i A)\,\times\Lift_i B}

  \inferrule*[lab=unit lifting]
             {}
             {\Lift_i\top = \top}
\end{mathpar}

@@

In Figure \ref{lifting}, we include an excerpt of cETT's rules. We change
presentation slightly from Sterling. We lift from $i$ to $i+j+1$ levels instead
of assuming $i < j$ and lifting to $j$, and we use a $\U_{\max(i,j)}$ return
type in functions and pairs, instead of having both $A$, $B$ types in the same
$\Set_i$. These changed rules are all derivable from the original ones. In
general, we can expect that lifting never impedes constructions, because it
appropriately computes out of the way.

@@

We also need to quantify over universe levels. cETT does not support this, and
we leave it like that. Instead, for the sake of simplicity, we quantify over
levels in an unspecified metatheory \emph{outside} cETT. Hence, a universe
polymorphic cETT term is understood as a $\mathbb{N}$-indexed family of
terms. We use the $\forall$ symbol for this, e.g.\ as $t : \forall\,i.\,\Set_i \ra
\Set_i$. This is sufficient in this paper, because we do not need to internalize
level-polymorphic constructions in cETT.

@@

\begin{nidefinition}{Notion of model for ToS.}\label{def:tos}
For levels $i$ and $j$, there is a cETT type $\ToS_{i,j} : \Set_{\max(i,\,j)+1}$, whose elements are
ToS models (or ToS-algebras). $\ToS_{i,j}$ is an iterated $\Sigma$-type, containing
all of the following components.
\begin{enumerate}
\item
  A category with families (CwF), where all four underlying sets (of
  objects, morphisms, types and terms) are in $\Set_j$. Following notation in
  \cite{TODO}, we denote these respectively as $\Con : \Set_j$, $\Sub : \Con \ra
  \Con \ra \Set_j$, $\Ty : \Con \ra \Set_j$ and $\Tm : (\Gamma : \Con) \ra
  \Ty\,\Gamma \ra \Set_j$. We denote the empty context as $\emptycon : \Con$,
  context extension as $\blank\ext\blank : (\Gamma : \Con)\ra \Ty\,\Gamma \ra \Con$.
  Substitution on types and terms is written as $\blank[\blank]$.
\item
  A universe $\U : \Ty\,\Gamma$ with decoding $\El : (a : \Tm\,\Gamma\,\U) \ra
  \Ty\,\Gamma$.
\item
  Inductive function space, with $\Pii : (a : \Tm\,\Gamma\,\U) \ra
  \Ty\,(\Gamma\,\ext\,\El\,a) \ra \Ty\,\Gamma$ and application as $\appi :
  \Tm\,\Gamma\,(\Pii\,a\,B)\ra \Tm\,(\Gamma\,\ext\,\El\,a)\,B$. We do not
  support $\lami$ here and in other function types, as they are not essential
  for QIIT signatures.
\item
  External function space with $\Set_i$ domain: $\Pie : (A : \Set_i)\ra(A \ra
  \Ty\,\Gamma)\ra \Ty\,\Gamma$, with $\appe : \Tm\,\Gamma\,(\Pie\,A\,B)\ra(x :
  A)\ra \Tm\,\Gamma\,(B\,x)$.
\item
  Infinitary function space, with $\Piinf : (A : \Set_i)\ra(A \ra
  \Tm\,\Gamma\,\U)\ra \Tm\,\Gamma\,\U$, $\appinf :
  \Tm\,\Gamma\,(\El\,(\Pie\,A\,b))\ra(x : A)\ra \Tm\,\Gamma\,(\El\,(b\,x))$.
\item
  An identity type $\Id : (a : \Tm\,\Gamma\,\U)\ra
  \Tm\,\Gamma\,(\El\,a)\ra\Tm\,\Gamma\,(\El\,a)\ra \Tm\,\Gamma\,\U$, with
  $\Refl : (T : \Tm\,\Gamma\,(\El\,a))\ra \Id\,a\,t\,t$, equality reflection
  and uniqueness of identity proofs.
\item
  An identity type $\IdU : \Tm\,\Gamma\,\U \ra \Tm\,\Gamma\,\U \ra \Ty\,\Gamma$, with
  evident $\ReflU$, equality reflection and uniqueness of identity proofs.
\end{enumerate}
\end{nidefinition}
In the above listing, we omit most CwF components and equations for substitution and
$\beta\eta$-conversion, but these should be understood to be also part of $\ToS_{i,j}$.

\emph{Notational conventions.} CwF components by default support de Bruijn
indices, which are not easily readable. We use instead a nameful notation for
binders in context extension, $\Pii$ and $\lami$, e.g.\ as $(\emptycon \ext a :
U \ext t : \El\,a)$. We also define a type-theoretic version of $\appi$ for
convenience:
\begin{alignat*}{3}
  & \blank\appitt\blank && :
      \Tm\,\Gamma\,(\Pii\,a\,B)\ra
      (u : \Tm\,\Gamma\,(\El\,a)) \ra \Tm\,\Gamma\,(B[id, u])\\
  & t\appitt u && :\equiv (\appi\,t)[id, u]
\end{alignat*}

\begin{nidefinition}{Notion of signature.}
A QIIT signature at level $i$ is a context in an arbitrary $M : \ToS_{i,j}$
model. We define the type of such signatures as follows:
\[
  \Sig_i :\equiv \forall j.\,(M : \ToS_{i,j})\ra M.Con
\]

Note that $\Sig_i$ is defined as a universe-polymorphic type, so it does not
have a type internally to cETT.

\begin{example}
The signature for natural
numbers is the following, where $\emptycon$, $\blank\ext\blank$, $\U$, $\El$ and
$\Pii$ all refer to components of the $\lambda$-bound $M$:
\begin{alignat*}{3}
  & NatSig : \Sig_0 \\
  & NatSig :\equiv \lambda (M : \ToS_{0,j}).\,(\emptycon\,\ext\, N : \U \,\ext\, zero : \El\,N \ext suc : \Pii\,(n : N)\,(\El\,N))
\end{alignat*}
\end{example}

The $i$ level in $\Sig_i$ specifies the level of the external types appearing in
a signatures, since the $\Pie$ and $\Piinf$ function spaces have domains in $\Set_i$.
In the case of naturals numbers, no external types appear, so the level of $NatSig$
can be chosen as $0$.

With this, we are able to specify QIITs, and we can also interpret each
signature in an arbitrary ToS model, by applying a signature to a model.
$\Sig_i$ can be viewed as a precursor to a Church-encoding for the theory of
signatures, but we only need contexts encoded in this way, and not other ToS
components. In functional programming, this encoding is sometimes called
``finally tagless''\cite{TODO}, and it is used for defining and interpreting
embedded languages.
\end{nidefinition}

@@

\begin{example}{Infinitary constructors}. The universe $\U$ is closed under
the $\Piinf$ function type, which makes it possible to write such functions in
the domains of $\Pii$ types. This allows a signature for trees branching with
arbitrary small sets. This is a signature at level 1, since we have $\Set_0$ as
domain type.
\[
TreeSig :\equiv
\emptycon \ext Tree : \U \ext node : \Pie\,\Set_0\,\lambda A.\,\Pii\,(\Piinf\,A\,\lambda \_.\,Tree)\,(\El\,Tree)
\]
\end{example}

@@

So, why do we use flCwF instead of lex categories? After all, the former
structure has more components and has more immediate complexity than the
latter. The reason is that flCwFs allow us to define induction in strictly the
same way as one would write it down in type theory, since we have $\Ty$ and
$\Tm$ for a primitive notion of dependent objects and morphisms. In contrast,
dependent objects in lex categories is a derived notion, and the induction
principles we get are what we want only up to isomorphisms. This issue is
perhaps not relevant from a purely categorical perspective, but we are concerned
with eventually implementing QIITs in proof assistants, so we prefer if our
semantics computes strictly.

\begin{nidefinition}{flCwF model for ToS.} We have for each $i$ and $j$ levels
an $M : \ToS_{i, 1+\max(i,j+1)}$ such that $M.\Con = \flCwF_{\max(i,j+1)}$. This
model is an extension to the CwF model of signatures in \cite{TODO}, with
$\Sigma$-types in the semantic CwF, the new type formers in signatures, and the
treatment of universe levels. We summarize the model below.
\begin{itemize}
\item As noted, $M.\Con = \flCwF_{\max(i,j+1)}$. The level $i$ marks the level of
      all external sets in function domains, and $j$ marks the level of all inductive
      sets in an algebra. Hence, every algebra, i.e.\ object of the flCwF, has
      level $\max(i,j+1)$. The bump is only needed for $j$, since algebras only contain
      \emph{elements} of $T : \Set_j$ types, while inductive sets are themselves elements
      of $\Set_i$. For example, $NatAlg_i : \Set_{\max(0, i+1)}$.
\item $\sigma : \Sub\,\Gamma\,\Delta$ substitutions are strictly structure-preserving flCwF
      functors.
    \item $A : \Ty\,\Gamma$ types are displayed flCwFs over $\Gamma$. This is an
      flCwF where every underlying set is indexed over underlying sets in
      $\Gamma$, and it is an extension of the displayed categories of Ahrens and
      Lumsdaine\cite{TODO}.  It contains equivalent data to an flCwF slice
      $\delta : \Sub\,\Delta\,\Gamma$. We prefer it to slices because it yields
      expected notions of induction strictly.
\item $t : \Tm\,\Gamma\,A$ terms are sections of the $A$ displayed flCwF. This can be viewed
      as a dependent functor, which maps structure in $\Gamma$ to corresponding displayed
      structure in $A$, e.g.\ it maps objects to displayed objects, morphisms to displayed
      morphisms, and so on.
\item $\emptycon : \Con$ is the terminal flCwF, whose underlying category is the terminal
      category with one object.

\item $\Gamma\,\ext\,A$ is the total flCwF of the $A$ displayed flCwF, where every underlying
      set is given by packing up indexed underlying sets of $A$ in $\Sigma$-s.

\item $\U : \Ty\,\Gamma$ is a displayed flCwF which is constantly (i.e. it does
      not depend on $\Gamma$) the flCwF of sets in $\Set_j$, whose underlying category
      is the usual category of sets.
\item
  $\Pii\,a\,B : \Ty\,\Gamma$ is a displayed flCwF where objects are
  dependent functions from the set of objects of $a$ to the set of objects of
  $B$. It is possible to build such flCwF because the $a : \Tm\,\Gamma\,\U$
  domain is discrete. A general $\Pii$ type is not possible because of variance
  issues; this is an extension of there being no $\Pii$ types in the category
  of categories\cite{elephant}
\item
  $\Pie\,A\,B : \Ty\,\Gamma$ is the $A$-indexed direct product of displayed flCwFs
  given by $B : A \ra \Ty\,\Gamma$.

\end{itemize}

%%   For $i$ and $j$ levels, there is
%% an $M : \ToS_{i, 1+\max(i,j+1)}$ such that $M.\Con = \flCwF_{\max(i,j+1)}$.
